Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-17 doc/manuscript/manuscript.Rmd
fix caps in Table 1

USA       MI     wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,       
                                              G122, Orion, PO7863, WM31

@@

USA       WA     wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008  cornell, G122, Orion, PO7      
                                              104, PO7863, WM31

                 producer          2003, 2007 GH, Merlot, Pinto, redkid    23

>>>>

USA       MI     wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, Cornell,       
                                              G122, Orion, PO7863, WM31

@@

USA       WA     wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008  Cornell, G122, Orion, PO7      
                                              104, PO7863, WM31

                 producer          2003, 2007 GH, Merlot, Pinto, Redkid    23
